---
title: "Assignment11"
author: "John Heinen"
date: "March 27, 2017"
output: html_document
---


## R Markdown Link <https://github.com/jheinen001/Assignment11/blob/master/Assignment11.Rmd>

#makes library(tseries) and library(forecast) available
```{r } 
library(tseries)
library(forecast)
```

#Download the data of SP500 '^gspc'
```{r } 
SNPdata <- get.hist.quote("^gspc",quote="Close")
```

#Calculate the log returns, which is the subtractration of log(lag(SNPdata)) and log(SNPdata)
```{r } 
SNPret <- log(lag(SNPdata)) - log(SNPdata)
```

#Calculate volatility measure that is to multiply sd(SNPret),sqrt(250), 100
```{r } 
SNPvol <- sd(SNPret)*sqrt(250)*100
```

## Define getVol function for volatility
```{r } 
getVol <- function(d, logrets) {
	var = 0
	lam = 0
	varlist <- c()

	for (r in logrets) {
		lam = lam*(1 - 1/d) + 1
	  var = (1 - 1/lam)*var + (1/lam)*r^2
		varlist <- c(varlist, var)
	}

	sqrt(varlist)
}
```


# Calculate volatility over entire length of series for various three different decay factors: 10 30. 100

#call getVol function with the parameters: 10,SNPret
```{r } 
volest <- getVol(10,SNPret)
```
#call getVol function with the parameters: 30,SNPret
```{r } 
volest2 <- getVol(30,SNPret)
```
#call getVol function with the parameters: 100,SNPret
```{r } 
volest3 <- getVol(100,SNPret)
```

## Plot
#Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
#Add connected line segments for volest2 with the parameters: type="l",col="red"
#Add connected line segments for volest3 with the parameters: type="l",col="blue"
```{r voltest, echo=FALSE}
plot(volest,type="l")
fit1 <- ses(volest2, h=3)
lines(fitted(fit1), col="red", type="l")
fit2 <- ses(volest3, h=3)
lines(fitted(fit2), col="blue", type="l")
```

